General limits

### 2017-09-18 papers/talk-7/paper-7.tex
fixed some typos

\maketitle
\section*{Introduction}
We have seen three special structures in categories,
the product, the pullback, and the equalizer.
As an example, the binary product is constructed in the following way.
We start with two objects. Then an object $U$ with maps to these objects is the product,
if it exists an satisfies the universal property for products, that is, all other such objects $V$
factor through $U$ uniquely.\\[1em]
\begin{minipage}{.26\linewidth}
  \begin{tikzcd}
    \bullet &&\bullet
  \end{tikzcd}
\end{minipage}%
\begin{minipage}{.1\linewidth}
  $\rightsquigarrow \quad$
\end{minipage}%
\begin{minipage}{.3\linewidth}
  \begin{tikzcd}
    & U \arrow{dl} \arrow{dr} &\\
    \bullet &&\bullet
  \end{tikzcd}
\end{minipage}%
\begin{minipage}{.1\linewidth}
  $\rightsquigarrow \quad$
\end{minipage}%
\begin{minipage}{.35\linewidth}
  \begin{tikzcd}
    & V \arrow[bend right=40]{ddl} \arrow[bend left=40]{ddr} \arrow[dashed]{d} &\\
    & U \arrow{dl} \arrow{dr} &\\
    \bullet &&\bullet
  \end{tikzcd}
\end{minipage}
\\[1em]
The pullback and the equalizer are constructed similarly.
They all have an input diagram, and we call an object $U$ with maps into this diagram
product/pullback/equalizer if it satisfies the universal property.
\\[1em]
\begin{minipage}{.35\linewidth}
  \begin{tikzcd}
    & V \arrow[bend right=40]{ddl} \arrow[bend left=40]{ddr} \arrow[dashed]{d} &\\
    & U \arrow{dl} \arrow{dr} &\\
    \bullet &&\bullet
  \end{tikzcd}
\end{minipage}%
\begin{minipage}{.35\linewidth}
  \begin{tikzcd}
    V
    \arrow[bend left=40]{drr}
    \arrow[bend right=40]{ddr}
    \arrow[dashed,swap]{dr}
    && \\
    &U
    \arrow{r}
    \arrow{d}
    &\bullet \arrow{d} \\
    & \bullet \arrow{r} & \bullet
  \end{tikzcd}
\end{minipage}%
\begin{minipage}{.3\linewidth}
  \begin{tikzcd}
    V \arrow[dashed]{dd} \arrow{dr}&& \\
    & \bullet \arrow[shift left]{r} \arrow[shift right]{r} & \bullet \\\
    U \arrow{ur} &&
  \end{tikzcd}
\end{minipage}\\[2em]
%% TODO: possibly give further applications of limits too
%% TODO: maybe some more intuition what limits are about

@@

In the following section we explain this definition. We need to clarify three things
in particular.
First we need to define the concept of a diagram more formally.
Then we define cones over a diagram. Lastly we state what it means for a cone
to be universal.
We start with diagrams. They are the initial entities of which we take the limit.
In the examples above the diagrams
are the various collections of objects (and arrows) that we start with
and over which the object $U$ has maps.

@@

The functor $D$ yields
a collection of objects and morphisms in the category $\mathscr C$
that looks just like $\bm I$.
We also say $D$ \textbf{identifies} diagrams of shape $\bm I$.
The shape category has no further meaning. Its only purpose
is to define how the diagram is supposed to look like.
The reason we use an intermediate
category $\bm I$ to define the shape is that
there might be many parts in $\mathscr C$ which have the shape $\bm I$,
especially when $\bm I$ is so small.
We therefore get all different diagrams of that shape by considering
all different functors $D$.
Diagrams do not necessarily have to be small. Their shape can even be infinite.
However most interesting diagrams tend to be very small.\\
We are typically interested in diagrams of a specific category,
$\mathscr C$ in the example. Therefore we usually leave out $\bm I$ and $D$,
and we just draw the identified part of $\mathscr C$ instead.\\
The next part on the way to the limit definition is the concept of a cone which
is what we address now.
\begin{definition}
  Let $D \from \bm{I} \to \mathscr{C}$ be a diagram.
  A \textbf{cone} $U$ over $D$ is an object $U \in \mathscr{C}$
  with maps $U \overset{f_I}{\rightarrow} D_I, \forall\ I \in \bm{I}$, such that
  $\forall\ I \overset{m}{\to} J \in \bm{I}$, the following triangle commutes:
  \[
    \begin{tikzcd}
      & U \arrow[dl, swap, "f_I"] \arrow{dr}{f_J}&\\
      D_I \arrow[rr, swap, "D_m"] & & D_J
    \end{tikzcd}
  \]
  That is, $f_J = D_m \circ f_I$.\\
  For a cone we write $(U \overset{f_I}{\to} D_I)_{I\in \bm{I}}$.
  We call $U$ the \textbf{vertex}, and $f_I$ the \textbf{projection maps} of the cone.
\end{definition}
\begin{remark}
  When it is clear from the context that $U$ is the vertex of a cone, then we use just
  the vertex $U$ to refer to the whole cone.
\end{remark}
\begin{example}
  A cone over the diagram of pullbacks
  (\hyperref[diagramexample]{Example \ref*{diagramexample}}) looks like this.
  \[
    \begin{tikzcd}
      U \arrow[bend right=30]{ddr}{f_I} \arrow[bend left=30]{drr}{f_K} \arrow[bend left=20, swap]{ddrr}{f_J}&   &\\
      & & D_K \arrow{d}{D_n} \\
      & D_I \arrow{r}{D_m} & D_J
    \end{tikzcd}
  \]
  The commuting condition says that $D_m \circ f_I = f_J$ and $D_n \circ f_K = f_J$.
\end{example}

@@

\begin{definition}
We say a category \textbf{has limits} over diagrams of shape $\bm I$, if for all
diagrams of shape $\bm I$, there exists a universal cone over it.
\end{definition}
A question that often arises is if a given category $\mathscr C$ has certain limits,
e.g. products or a terminal object. Now that we have a abstract definition of limits
we can approach this problem in a more systematic way.
This leads to two observations:\\
\hyperref[equiinstance]{(\ref*{equiinstance})} A category $\mathscr C$ has finite products and equalizers iff
it has pullbacks and a terminal
object.\\
\hyperref[arbitrarylimits]{(\ref*{arbitrarylimits})}
If a category $\mathscr C$ has products and equalizers, then it has all limits, that is,
limits of diagrams of arbitrary shape can be constructed using these two instances.

\subsection{Products}
So far we have only been concerned with the product of two objects, i.e. the binary product.
We now study the concept of products more generally.
\begin{lemma}
  \label{emptyproduct}
  The empty product, i.e. the product of zero objects, is a terminal objects
\end{lemma}
\begin{proof}
  The empty product is a limit over the empty diagram just as the terminal object
  as discussed in
  \hyperref[terminallimit]{Example \ref*{terminallimit}}
\end{proof}

@@

\begin{lemma}
  \label{finiteproducts}
  Let $\mathscr C$ be a category with a terminal object $1$ and binary products.
  Then we can construct all finite products.
\end{lemma}
\begin{proof}
  The idea is to first show the existence of the empty and the unary product.
  For larger products we stack binary products on top of each other.
  \begin{itemize}
  \item The empty product is just the terminal object by
    \hyperref[emptyproduct]{Example \ref*{emptyproduct}}
  \item The unary product of any object $A$ is constructed from the binary product
    $A \times 1$.
    We have maps $1_A \from A \to A$, $\pi_A \from A \times 1 \to A$, and $\pi_1 \from A \times 1 \to 1$.
    Every other object $B$ has a unique map $t_B \from B \to 1$. If $B$ has a map $f \from B \to A$, then
    it factors uniquely through $A \times 1$ by the universal property of products.
  \item The binary product exists by assumption for all objects $A, B$.
  \item We build some finite product over objects $D_1, \dots D_k$.
    Assume by induction that the following two smaller products exist.
    \[ P_1 \coloneqq \displaystyle \prod_{i \in \{1, \dots, \frac{k}{2} \} } D_i \text{ , and } P_2 \coloneqq \displaystyle \prod_{i \in \{\frac{k}{2} + 1, \dots, k\} } D_i \]
    with projection maps $(\pi_i)_{i \in \{1, \dots, \frac{k}{2} \} }$ for $P_1$, and $(\tau_i)_{i \in \{\frac{k}{2}+1, \dots, k\} }$ for $P_2$.
    Then there exists a binary product of $P_1 \times P_2$ with projection maps $f_{P_1}, f_{P_2}$.
    $P_1 \times P_2$ has maps $\pi_i \circ f_{P_1}$ and $\tau_i \circ f_{P_2}$.
    $P_1 \times P_2$ is therefore a cone.
    Since $P_1$ and $P_2$ are products, any other cone $V$ over them has unique maps $h_{P_1}$ and $h_{P_2}$.
    The unique morphism $V \rightarrow P_1 \times P_2$ is given by $\langle h_{P_1}, h_{P_2} \rangle$.
    $P_1 \times P_2$ is therefore universal.
  \end{itemize}
\end{proof}

@@

In this section we establish that the instances of limits we have seen are related
in a way that allows us to show how to construct these instances using others.
This implies that if we know that a category has some of the right instances
we can construct other limits for free using only category theoretical arguments.

@@

\begin{theorem}
  \label{arbitrarylimits}
  Let $\mathscr C$ be a category that has all (finite) products and equalizers.
  Let $D : \bm I \to \mathscr C$ be a (finite) diagram.
  Then we can construct a limit of $D$.
\end{theorem}
\begin{proof}
We use the following construction:
\[
  \begin{tikzcd}
    E \arrow{r}{e} &
    \displaystyle \prod_{I \in \bm{I}} D_I
    \arrow[r,shift left, "s"] \arrow[r,shift right,swap,"t"] &
    \displaystyle \prod_{K \overset{n}{\to} J \in \bm{I}} D_J
  \end{tikzcd}
\]
with the maps $s, t$ that have components $s_n, t_n$ for all $K \overset{n}{\to} J \in \bm{I}$:
\begin{align*}
  s_n &= Dn \circ p_K\ \hat{=} \prod_{I \in \bm{I}} D_I
        \overset{p_K}{\rightarrow} D_K \overset{Dn}{\rightarrow} D_J \\
  t_n &= p_J\ \hat{=} \prod_{I \in \bm{I}} D_I
        \overset{p_J}{\rightarrow} D_J
\end{align*}

The product $\displaystyle \prod_{K \overset{n}{\to} J \in \bm{I}} D_J$ has components for each map in the diagram.
We take the diagram for pullbacks as an example:
\begin{tikzcd}
 I \arrow{r}{m} & J & \arrow[swap]{l}{n} K
\end{tikzcd}.
For this example diagram the product has the following projections. One for each identity:
$p_{1_I} \from \prod \to I,\ p_{1_J} \from \prod \to J,\ p_{1_K} \from \prod \to K$,
and one for each remaining map in the diagram: $p_m \from \prod \to J,\ p_n \from \prod \to J$.\\
All products in the above construction exist by assumption.
We take $E$ as the equalizer of $s$ and $t$ which also exists by assumption.
We therefore have $s \circ e = t \circ e$.
The maps $s$ and $t$ have components. The equality has to hold for all
components and we get
\begin{align*}
  s \circ e &= t \circ e\\
  s_n \circ e &= t_n \circ e, \quad \forall\ K \overset{n}{\rightarrow} J \in \bm I \\
  Dn \circ p_K \circ e &= p_J \circ e
\end{align*}
With this setup we show that we have a universal cone over $D$.
We take $E$ as the vertex and
$\uprho_I \coloneqq p_I \circ e, \forall\ I \in \bm I$
as the projection maps of the cone.
Clearly, we have all necessary projection maps and we only need to verify
the commuting condition of cones.
We have all maps $K \overset{n}{\rightarrow} J \in \bm I$
\begin{align*}
  Dn \circ p_K \circ e &= p_J \circ e \\
  Dn \circ \uprho_K &= \uprho_J
\end{align*}
which corresponds to the commuting diagram
\[
  \begin{tikzcd}
    E \arrow{r}{\uprho_K} \arrow{dr}[swap]{\uprho_J} & D_K \arrow{d}{Dn}\\
    & D_J
  \end{tikzcd}
\]
This is exactly the commuting condition we need for a cone.\\
Since any other cone over $D$
is also a fork of $s$ and $t$
it follows that the equalizer $E$ is also a universal cone,
that is, a limit of $D$.
\end{proof}
\begin{remark}
  If $\mathscr C$ has all products including infinite products then
  this construction works even for infinite diagrams.
  If $\mathscr C$ only has finite products, then we can
  use this construction for
  limits of finite diagrams.
\end{remark}

>>>>

\maketitle
\section*{Introduction}
We have seen three special structures in categories,
the product, the pullback, and the equalizer.
As an example, the binary product is constructed in the following way.
We start with two objects. Then an object $U$ with maps to these objects is the product,
if it exists and satisfies the universal property for products, that is, all other such objects $V$
factor through $U$ uniquely.\\[1em]
\begin{minipage}{.26\linewidth}
  \begin{tikzcd}
    \bullet &&\bullet
  \end{tikzcd}
\end{minipage}%
\begin{minipage}{.1\linewidth}
  $\rightsquigarrow \quad$
\end{minipage}%
\begin{minipage}{.3\linewidth}
  \begin{tikzcd}
    & U \arrow{dl} \arrow{dr} &\\
    \bullet &&\bullet
  \end{tikzcd}
\end{minipage}%
\begin{minipage}{.1\linewidth}
  $\rightsquigarrow \quad$
\end{minipage}%
\begin{minipage}{.35\linewidth}
  \begin{tikzcd}
    & V \arrow[bend right=40]{ddl} \arrow[bend left=40]{ddr} \arrow[dashed]{d} &\\
    & U \arrow{dl} \arrow{dr} &\\
    \bullet &&\bullet
  \end{tikzcd}
\end{minipage}
\\[1em]
The pullback and the equalizer are constructed similarly.
They all have an input diagram, and we call an object $U$ with maps into this diagram
product/pullback/equalizer if makes the diagram commute and satisfies the universal property.
\\[1em]
\begin{minipage}{.35\linewidth}
  \begin{tikzcd}
    & V \arrow[bend right=40]{ddl} \arrow[bend left=40]{ddr} \arrow[dashed]{d} &\\
    & U \arrow{dl} \arrow{dr} &\\
    \bullet &&\bullet
  \end{tikzcd}
\end{minipage}%
\begin{minipage}{.35\linewidth}
  \begin{tikzcd}
    V
    \arrow[bend left=40]{drr}
    \arrow[bend right=40]{ddr}
    \arrow[dashed,swap]{dr}
    && \\
    &U
    \arrow{r}
    \arrow{d}
    &\bullet \arrow{d} \\
    & \bullet \arrow{r} & \bullet
  \end{tikzcd}
\end{minipage}%
\begin{minipage}{.3\linewidth}
  \begin{tikzcd}
    V \arrow[dashed]{dd} \arrow{dr}&& \\
    & \bullet \arrow[shift left]{r} \arrow[shift right]{r} & \bullet \\\
    U \arrow{ur} &&
  \end{tikzcd}
\end{minipage}\\[2em]
%% TODO: possibly give further applications of limits too
%% TODO: maybe some more intuition what limits are about

@@

In the following section we explain this definition. We need to clarify three things for this.
First we need to define the concept of a diagram more formally.
Then we define cones over a diagram. Lastly we state what it means for a cone
to be universal.
We start with diagrams. They are the initial entities of which we take the limit.
In the examples above the diagrams
are the various collections of objects (and arrows) that we start with.

@@

The functor $D$ yields
a collection of objects and morphisms in the category $\mathscr C$
that looks just like $\bm I$.
We also say $D$ \textbf{identifies} diagrams of shape $\bm I$.
The shape category has no further meaning. Its only purpose
is to define how the diagram is supposed to look like.
The reason we use an intermediate
category $\bm I$ to define the shape is that
there might be many parts in $\mathscr C$ which have the shape $\bm I$,
especially when $\bm I$ is small.
We therefore get all different diagrams of that shape by considering
all different functors $D$.
Diagrams do not necessarily have to be small. Their shape can even be infinite.
However most interesting diagrams tend to be very small.\\
We are typically interested in diagrams of a specific category,
$\mathscr C$ in the example. Therefore we usually leave out $\bm I$ and $D$,
and we just draw the identified part of $\mathscr C$ instead.\\
The next part on the way to the limit definition is the concept of a cone which
is what we address now.
\begin{definition}
  Let $D \from \bm{I} \to \mathscr{C}$ be a diagram.
  A \textbf{cone} $U$ over $D$ is an object $U \in \mathscr{C}$
  with maps $U \overset{f_I}{\rightarrow} D_I, \forall\ I \in \bm{I}$, such that
  $\forall\ I \overset{m}{\to} J \in \bm{I}$, the following triangle commutes:
  \[
    \begin{tikzcd}
      & U \arrow[dl, swap, "f_I"] \arrow{dr}{f_J}&\\
      D_I \arrow[rr, swap, "D_m"] & & D_J
    \end{tikzcd}
  \]
  That is, $f_J = D_m \circ f_I$.\\
  For a cone we write $(U \overset{f_I}{\to} D_I)_{I\in \bm{I}}$.
  We call $U$ the \textbf{vertex}, and $f_I$ the \textbf{projection maps} of the cone.
\end{definition}
\begin{remark}
  When it is clear from the context that $U$ is the vertex of a cone, then we use just
  the vertex $U$ to refer to the whole cone.
\end{remark}
\begin{example}
  A cone over the diagram of pullbacks
  (\hyperref[diagramexample]{Example \ref*{diagramexample}}) looks like this.
  \[
    \begin{tikzcd}
      U \arrow[bend right=30]{ddr}{f_I} \arrow[bend left=30]{drr}{f_K} \arrow[bend left=20, swap]{ddrr}{f_J}&   &\\
      & & D_K \arrow{d}{D_n} \\
      & D_I \arrow{r}{D_m} & D_J
    \end{tikzcd}
  \]
  The commuting condition says that $D_m \circ f_I = f_J$ and $D_n \circ f_K = f_J$.
\end{example}

@@

\begin{definition}
We say a category \textbf{has limits} over diagrams of shape $\bm I$, if for all
diagrams of shape $\bm I$, there exists a universal cone over it.
\end{definition}
A question that often arises is if a given category $\mathscr C$ has certain limits,
e.g. products or a terminal object. Now that we have a abstract definition of limits
we can approach this problem in a more systematic way.
This leads to two observations:\\
\hyperref[equiinstance]{Section \ref*{equiinstance}:} A category $\mathscr C$ has finite products and equalizers iff
it has pullbacks and a terminal
object.\\
\hyperref[arbitrarylimits]{Section \ref*{arbitrarylimits}:}
If a category $\mathscr C$ has products and equalizers, then it has all limits, that is,
limits of diagrams of arbitrary shape can be constructed using these two instances.

\subsection{Products}
So far we have only been concerned with the product of two objects, i.e. the binary product.
We now study the concept of products more generally.
\begin{lemma}
  \label{emptyproduct}
  The empty product, i.e. the product of zero objects, is a terminal object.
\end{lemma}
\begin{proof}
  The empty product is a limit over the empty diagram just as the terminal object
  as discussed in
  \hyperref[terminallimit]{Example \ref*{terminallimit}}
\end{proof}

@@

\begin{lemma}
  \label{finiteproducts}
  Let $\mathscr C$ be a category with a terminal object $1$ and binary products.
  Then we can construct all finite products.
\end{lemma}
\begin{proof}
  The idea is to first show the existence of the empty and the unary product.
  For larger products we stack binary products on top of each other.
  \begin{itemize}
  \item The empty product is just the terminal object by
    \hyperref[emptyproduct]{Lemma \ref*{emptyproduct}}
  \item The unary product of any object $A$ is constructed from the binary product
    $A \times 1$.
    We have maps $1_A \from A \to A$, $\pi_A \from A \times 1 \to A$, and $\pi_1 \from A \times 1 \to 1$.
    Every other object $B$ has a unique map $t_B \from B \to 1$. If $B$ has a map $f \from B \to A$, then
    it factors uniquely through $A \times 1$ by the universal property of products.
  \item The binary product exists by assumption for all objects $A, B$.
  \item We build some finite product over objects $D_1, \dots D_k$.
    Assume by induction that the following two smaller products exist.
    \[ P_1 \coloneqq \displaystyle \prod_{i \in \{1, \dots, \frac{k}{2} \} } D_i \text{ , and } P_2 \coloneqq \displaystyle \prod_{i \in \{\frac{k}{2} + 1, \dots, k\} } D_i \]
    with projection maps $(\pi_i)_{i \in \{1, \dots, \frac{k}{2} \} }$ for $P_1$, and $(\tau_i)_{i \in \{\frac{k}{2}+1, \dots, k\} }$ for $P_2$.
    Then there exists a binary product of $P_1 \times P_2$ with projection maps $f_{P_1}, f_{P_2}$.
    $P_1 \times P_2$ has maps $\pi_i \circ f_{P_1}$ and $\tau_i \circ f_{P_2}$.
    $P_1 \times P_2$ is therefore a cone.
    Since $P_1$ and $P_2$ are products, any other cone $V$ over them has unique maps $h_{P_1}$ and $h_{P_2}$.
    The unique morphism $V \rightarrow P_1 \times P_2$ is given by $\langle h_{P_1}, h_{P_2} \rangle$.
    $P_1 \times P_2$ is therefore universal.
  \end{itemize}
\end{proof}

@@

In this section we establish that the instances of limits we have seen are related
in a way that allows us to construct some instances using others.
This implies that in any category which has the right instances
we can construct other limits for free using only category theoretical arguments.

@@

\begin{theorem}
  \label{arbitrarylimits}
  Let $\mathscr C$ be a category that has all products and equalizers.
  Let $D : \bm I \to \mathscr C$ be a diagram.
  Then we can construct a limit of $D$.
\end{theorem}
\begin{proof}
We use the following construction:
\[
  \begin{tikzcd}
    E \arrow{r}{e} &
    \displaystyle \prod_{I \in \bm{I}} D_I
    \arrow[r,shift left, "s"] \arrow[r,shift right,swap,"t"] &
    \displaystyle \prod_{K \overset{n}{\to} J \in \bm{I}} D_J
  \end{tikzcd}
\]
with the maps $s, t$ that have components $s_n, t_n$ for all $K \overset{n}{\to} J \in \bm{I}$:
\begin{align*}
  s_n &= Dn \circ p_K\ \hat{=} \prod_{I \in \bm{I}} D_I
        \overset{p_K}{\rightarrow} D_K \overset{Dn}{\rightarrow} D_J \\
  t_n &= p_J\ \hat{=} \prod_{I \in \bm{I}} D_I
        \overset{p_J}{\rightarrow} D_J
\end{align*}

The product $\displaystyle \prod_{K \overset{n}{\to} J \in \bm{I}} D_J$ has components for each map in the diagram.
To clarify this, we take the diagram for pullbacks as an example:
\begin{tikzcd}
 I \arrow{r}{m} & J & \arrow[swap]{l}{n} K
\end{tikzcd}.
For this diagram the product has the following projections. One for each identity:
$p_{1_I} \from \prod \to I,\ p_{1_J} \from \prod \to J,\ p_{1_K} \from \prod \to K$,
and one for each remaining map in the diagram: $p_m \from \prod \to J,\ p_n \from \prod \to J$.\\
All products in the above construction exist by assumption.
We take $E$ as the equalizer of $s$ and $t$ which also exists by assumption.
We therefore have $s \circ e = t \circ e$.
The maps $s$ and $t$ have components. The equality has to hold for all
components and we get
\begin{align*}
  s \circ e &= t \circ e\\
  s_n \circ e &= t_n \circ e, \quad \forall\ K \overset{n}{\rightarrow} J \in \bm I \\
  Dn \circ p_K \circ e &= p_J \circ e
\end{align*}
With this setup we show that we have a universal cone over $D$.
We take $E$ as the vertex and
$\uprho_I \coloneqq p_I \circ e, \forall\ I \in \bm I$
as the projection maps of the cone.
Clearly, we have all necessary projection maps. Now we need to verify
the commuting condition.
We have for all maps $K \overset{n}{\rightarrow} J \in \bm I$
\begin{align*}
  Dn \circ p_K \circ e &= p_J \circ e \\
  Dn \circ \uprho_K &= \uprho_J
\end{align*}
which corresponds to the commuting diagram
\[
  \begin{tikzcd}
    E \arrow{r}{\uprho_K} \arrow{dr}[swap]{\uprho_J} & D_K \arrow{d}{Dn}\\
    & D_J
  \end{tikzcd}
\]
This is exactly the commuting condition we need for a cone.\\
Since any other cone over $D$
is also a fork of $s$ and $t$
it follows that the equalizer $E$ is also a universal cone,
that is, a limit of $D$.
\end{proof}
\begin{remark}
  If $\mathscr C$ has all products including infinite products then
  this construction works even for infinite diagrams.
  If $\mathscr C$ only has finite products, then we can
  use this construction for
  limits of finite diagrams.
\end{remark}
